\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-08 manuscript/main.tex
new file:   Plotting of Sample Distribution/GpMessages/2616494096400 	new file:   Plotting of Sample Distribution/ImportLog/55c4de46096847c88b832e57b051473d_Import.xml 	new file:   Plotting of Sample Distribution/ImportLog/9cdfaa0a4cd74623bd00534f923a7525_Import.xml 	new file:   Plotting of Sample Distribution/ImportLog/b6386bc1a434430fbca275b5770f744a_Import.xml 	new file:   Plotting of Sample Distribution/Plotting of Sample Distribution.aprx 	new file:   Plotting of Sample Distribution/Plotting of Sample Distribution.atbx 	new file:   Plotting of Sample Distribution/Plotting of Sample Distri

\documentclass[11pt]{article}
\usepackage[right=1in,left=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{graphicx}
\usepackage{url}
\usepackage{adjustbox}
\usepackage[round]{natbib}
\usepackage{amsmath,amsthm}
\usepackage{engord}
\usepackage{float}
\usepackage{subfig}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{endnotes}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfig}
\pgfplotsset{compat=1.14}
\usepackage{longtable}
\pgfplotsset{every axis label/.append style={font=\tiny}}
\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"
\usepackage{authblk}
\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
\usepackage{multirow} %% Necessary if we are doing tables in LaTeX

@@

@@

\section{Appendix Tables and Figures}

@@

  This photo was taken in Chengdu, where Lianjia operates over 1,500 offline stores. It is common to see two stores located within a short distance of each other. The green store in the photo is one of Lianjia's offline stores. As you can see, across the street, there are two Lianjia stores, each managed by different store managers. 
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/distribution_of_ten_cities.pdf}
  \caption{Distribution of Ten Cities's Brokerages Store Shares}
  \label{fig:distribution_store_shares}
  Note: the x-axis is city's name and the y-axis is the offline brokerage's stores share in the city. The data source is from AutoNavi Map.
\end{figure}

% \input{tab_tex/other-regressions.tex}

@@

\input{../result_tables/donut_robust.tex}

@@

>>>>

\documentclass[11pt]{article}
\usepackage[right=1in,left=1in,top=1in,bottom=1in]{geometry}
\usepackage{hyperref}
\hypersetup{colorlinks, citecolor=blue, filecolor=blue, linkcolor=blue, urlcolor=blue}
\usepackage{graphicx}
\usepackage{url}
\usepackage{adjustbox}
\usepackage[round]{natbib}
\usepackage{amsmath,amsthm}
\usepackage{engord}
\usepackage{float}
\usepackage{subfig}
\usepackage{pdflscape}
\usepackage{booktabs}
\usepackage{endnotes}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfig}
\pgfplotsset{compat=1.14}
\pgfplotsset{every axis label/.append style={font=\tiny}}
\usepackage[labelsep=period]{caption} %% This switches "Table 1: Title" to "Table 1. Title"
\usepackage{authblk}
\usepackage{amssymb} %% Necessary, just for the \checkmark command  in tables.
\usepackage{multirow} %% Necessary if we are doing tables in LaTeX

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% APPENDIX

@@

\section{Additional Descriptions of Data} \label{sec:appendix_data}

@@

  This photo was taken in Chengdu, where Lianjia operates over 1,500 offline stores. It is common to see two stores located within a short distance of each other. The green store in the photo is one of Lianjia's offline stores. As you can see, across the street, there are two Lianjia stores, each managed by different store managers. This phenomenon is very common in large Chinese cities and can be found in many markets, see for example Figure \ref{fig:typical_layout_Beijing}.
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/typical_layout_beijing.pdf}
  \caption{Sample of Lianjia's Offline Stores in Beijing}
  \label{fig:typical_layout_Beijing}

This figure illustrates the spatial distribution of Lianjia's offline stores in Beijing for the year 2021. The data reveals a significant clustering of stores around major residential buildings, demonstrating a high degree of localization within the real estate brokerage market. This pattern is indicative of the competitive dynamics and agglomeration economies prevalent in the Chinese real estate sector, where proximity to key infrastructure. The data source is from AutoNavi Map.
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/distribution_of_ten_cities.pdf}
  \caption{Distribution of Ten Cities's Brokerages Store Shares}
  \label{fig:distribution_store_shares}

  Note: the x-axis is city's name and the y-axis is the offline brokerage's stores share in the city. The data source is from AutoNavi Map.
\end{figure}

\section{Additional RDD Robustness Tests} \label{sec:additional_rdd}
% \input{tab_tex/other-regressions.tex}

Table \ref{}
\input{../result_tables/donut_robust.tex}

@@

\section{Placebo Test}

\begin{figure}[H]
  \centering
  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_num.pdf}\label{fig:placebo_num_entry}}
  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_lead.pdf}\label{fig:placebo_lead_entry}}
  \hfill % Adds horizontal space between figures
  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_period.pdf}\label{fig:placebo_period_entry}}
  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_entry_concession.pdf}\label{fig:placebo_concession_entry}}
  \caption{Placebo Test to Entry Effect}
  \label{fig:placebo_test_entry}

  Note: The x-axis is the coefficient of the

  the model is described in Equation \eqref{eq:entry_effect}
  \end{figure}

\begin{figure}[H]
  \centering
  \subfloat[Placebo Test to transaction number]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_num.pdf}\label{fig:placebo_num_plat}}
  \subfloat[Placebo Test to number of house tours]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_lead.pdf}\label{fig:placebo_lead_plat}}
  \hfill % Adds horizontal space between figures
  \subfloat[Placebo Test to transaction period]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_period.pdf}\label{fig:placebo_period_plat}}
  \subfloat[Placebo Test to price concession]{\includegraphics[width=0.45\textwidth]{../figures/placebo_results/placebo_plat_concession.pdf}\label{fig:placebo_concession_plat}}
  \caption{Placebo Test to Platform-Mediated Consolidation Effect}
  \label{fig:placebo_test_plat}

  Note: The x-axis is the coefficient of the

  the model is described in Equation \eqref{eq:acn_assessment}

\end{figure}
